Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-30 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:30	20:44:00	(Wed30.Sep)

Throughout this article we have used LCA with variations of the Kaiser window function defined in (\ref{kaiser_window_element}), steered in . However, as shown in \Fig{image_quality} we can obtain similar performance using the trigonometric window function:

\ref{trig_window_function} \ref{steering_window}

%
\begin{align}
f_m(\alpha) = e^{j\phi_\theta[m]}\Big[\alpha - (1-\alpha)\cos\Big(\frac{2\pi m}{M-1}\Big)\Big]\label{trig_window_function}
\end{align}
%
(\ref{steering_vector})
where $\phi_\theta[m] = \frac{2\pi}{\lambda}dm\sin\theta$ is the steering angle. For this window there is an analytic solution for the optimal value of $\alpha$ in the minimum variance sense. To derive it, we start by inserting the window function (\ref{trig_window_function}) into the beamformer equation (\ref{z}):
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\Big(\alpha - (1-\alpha)\cos\left(\frac{2\pi m}{M-1}\right)\Big) x_m^* \nn
&= \alpha \a\T\x + (1-\alpha)\b\T\x
\end{align}
%
where $\a$ is the steering vector defined in (\ref{steering_vector}), and 
%
\begin{align}
\b = \text{diag}(\a)\cdot\begin{bmatrix}
     1 &
     \cos\left(\frac{2\pi}{M-1}\right) &
     \cos\left(\frac{2\pi 2}{M-1}\right) &
     \hdots &
     1
     \end{bmatrix}\T.
\end{align}
%
To attain unity gain in the look direction the weights must sum to one:
%
\begin{align}
\w\T\1 &= \big(\alpha\a - (1-\alpha)\b\big)\T\1 = 1
\end{align}
%
This is true for any value of $\alpha$ if $\a\T\1 = 1$ and $\b\T\1 = 1$. Hence, we can preserve the unity gain constraint as long as we normalize $\a$ and $\b$.

>>>>

Throughout this article we have used LCA with variations of the Kaiser window function defined in (\ref{kaiser_window_element}), steered as described in (\ref{steered_window}). However, as shown in \Fig{image_quality} we can obtain similar performance using the trigonometric window function defined in (\ref{trig_window_function} ):
%
\begin{align}
f_m(\alpha) = e^{j\theta_\phi[m]}\Big[\alpha - (1-\alpha)\cos\Big(\frac{2\pi m}{M-1}\Big)\Big]\label{trig_window_function}
\end{align}
%
where $\theta_\phi[m] = \frac{2\pi dm}{\lambda}\sin\phi$ is the $m$th component of the steering vector defined in (\ref{steering_vector}). For this window there is an analytic solution for the optimal value of $\alpha$ in the minimum variance sense. To derive it, we start by inserting the window function (\ref{trig_window_function}) into the beamformer equation (\ref{z}):
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\theta_\phi[m]}\Big(\alpha - (1-\alpha)\cos\left(\frac{2\pi m}{M-1}\right)\Big) x_m^* \nn
&= \alpha \a\T\x - (1-\alpha)\b\T\x
\end{align}
%
where $\a$ is the steering vector defined in (\ref{steering_vector}), and 
%
\begin{align}
\b = \text{diag}(\a)\cdot\begin{bmatrix}
     1 &
     \cos\left(\frac{2\pi}{M-1}\right) &
     \cos\left(\frac{2\pi 2}{M-1}\right) &
     \hdots &
     1
     \end{bmatrix}\T.
\end{align}
%
To attain unity gain in the look direction the weights must sum to one:
%
\begin{align}
\w\T\1 &= \big(\alpha\a - (1-\alpha)\b\big)\T\1 = 1
\end{align}
%
This is true for any value of $\alpha$ if $\a\T\1 = 1$ and $\b\T\1 = 1$. Hence, we can preserve the unity gain constraint as long as we normalize $\a$ and $\b$.
